---
title: "Interfacing with ERIC"
author: "Tim Ransom"
date: "10/22/2021"
output: html_document
runtime: shiny
---
<!-- We need to remove this to include in the user interface -->
<!-- ```{r setup, include=FALSE} -->
<!-- knitr::opts_chunk$set(echo = TRUE) -->
<!-- ``` -->

## Search terms

We're representing our search terms as a list of lists, where the top level elements
are AND'd and the lower level elements are OR'd. For example: ((a, b, c), (d, e))
represents "a OR b OR c" AND "d OR e"

Here's the full list of terms we're going to make our queries out of:
```{r}
search_terms <- list(list("community college", "higher education", "postsecondary education"),
                     list("pandemic", "COVID-19"),
                     list("online courses", "online learning",
                        "educational technology", "distance education", "electronic learning"),
                     list("hands on", "lab"),
                     list("FAA", "part 147"))

test_searh_terms <- list(list("community college", "higher education"),
                         list("online learning", "distance education"))
```


## Powerset construction

We need to try all the combinations of our search terms, which mathematically
is the cartesian product of the powersets of our full list above.

A table showing the cartesian product of the search "(a OR b) AND (1 OR 2)"
```{text}
|    | a   | b   | ab   |     "" |
|  1 | a1  | b1  | ab1  |      1 |
|  2 | a2  | b2  | ab2  |      2 |
| 12 | a12 | b12 | ab12 |     12 |
| "" | a   | b   | ab   | REMOVE |
```

```{r}

decimal_to_binary_list <- function(number) {
  if (number == 0) {
    return(list(0))
  }
  
  out <- list()
  len <- 1
    
  while (number >= 1) {
    out[[len]] <- floor(number %% 2)
    number <- floor(number / 2)
    len <- len + 1
  }
  
  return(out)
}

binary_mask <- function(set, binary_string) {
  if (all(binary_string == 0)) {
    return(list(""))
  }
  
  out <- list()
  
  i <- 1
  
  for (bit in binary_string) {
    if (bit == 1) {
      out[[length(out) + 1]] <- set[[i]]
    }
    i <- i + 1
  }
  
  return(out)
}

powerset <- function(set) {
  set_as_list <- as.list(set)
  
  out <- list()
  
  for (i in 0:(2^length(set)-1)) {
     out[[length(out) + 1]] <- binary_mask(set_as_list, decimal_to_binary_list(i))
  }
  
  return(out)
  
}

term_powerset <- function(search_terms) {
  # Create the powersets and convert empty values to empty vector
  rapply(mapply(powerset, search_terms), function(x) {
    if (length(x) == 0) {
      return(c(""))
    } else {
      return(x)
    }
  }, how = "replace")
}

format_powerset <- function(powerset) {
  # We turn the powersets into a one dimensional list so we can format each set with a special string in between
  # This can be changed but we don't want to use something common because we'll need to split on it later.
  
  if (class(powerset[[1]][[1]]) == "list") {
    powerset <- unlist(powerset, recursive = FALSE)
  }
  
  compacted_list <- mapply(function(x) { paste(x, collapse = "```") }, powerset)
  
  # We then need to split the list by empty strings so that we can use each powerset individually
  
  split(compacted_list, cumsum(data.frame(compacted_list)[, 1] == ""))
}
```


## ERIC communications

### Utility functions
We use a couple functions to talk to the ERIC api, one to format the query for
the database request and one to talk to ERIC.

```{r}
get_eric_json <- function(encoded_url) {
  library(curl)
  library(rjson)

  # variable left out for future caching opportunity
  req <- curl_fetch_memory(encoded_url)
  return(fromJSON(rawToChar(req$content)))
}


# All possible fields can be found here: https://eric.ed.gov/?api#/default/get_eric_
# possible interesting additions: language, publicationtype, publicationdateyear
# magic numbers:
#   rows - max ERIC lets one pull to API be
#   start - adjust to daisy-chain queries together when there are more than 2000 (unimplemented)
create_eric_url <- function(search_terms, start = 0, rows = 2000,
                            fields = list(list("*"), list("peerreviewed", "'T'"))) {

  # unlikely to change, we only care about ERIC at the moment
  eric_base_url <- "https://api.ies.ed.gov/eric/"
  # we've selected json over xml for parsing and efficiency purposes
  format <- "json"
  
  # two one liners to form our search term logical expression and the field modification encoding
  formatted_terms <- paste(mapply(function(x) {paste(unlist(x), collapse = " OR ")}, search_terms), collapse = " AND ")
  formatted_fields <- paste(mapply(function(x) {paste(unlist(x), collapse = ":")}, fields), collapse = " ")
  
  unencoded_url <- paste(eric_base_url, 
                           "?search=", formatted_terms, 
                           "&format=", format, 
                           "&start=", start,
                           "&rows=", rows, 
                           "&fields=", formatted_fields, 
                           sep = "")
  
  return(URLencode(unencoded_url)) # urltools::url_encode broke api compatibility, using utils::URLencode instead
}
```

### Talking to ERIC

Here's the putting-it-all-together for this file. I've just put in some untested
skeleton code here of how I see it fitting together. This is the last backend task before
we jump into the GUI reactive stuff.

```{r}
#all_eric_term_queries <- "" # TODO: use smaller test terms, term_powerset(test_search_terms)
#all_eric_urls <- "" # TODO: map the list of searchs through create_eric_url
#all_eric_json_results <- list() # TODO: this is likely better represented with an R dataframe, if so, should we convert after all api queries or during loop?

# TODO: is this better iteratively or can we do some parallel network hits? I don't see ERIC docs talking about that
# for (eric_url in all_eric_urls) {
  # TODO: write some of these to files that we can use for testing
  # eric_json <- get_eric_json(eric_url)

  # all_eric_json_results.append(eric_json)
# }

# print out the human readable version of the search query and the number of results for it
# just a two column list to STDOUT is good for now, just want to see it somewhere other than the R env
```
